Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2020-03-21 write-up/fda-recurrent.tex
update sims and tex to match

\begin{table}[!th]
\begin{tabular}{c | c c c c c}
Sampling rate & 0.5 & 1 & 5 & 25 & 50 \\ \hline
Variance & (10,12) & - & - & - & - \\
Squared Bias & - & - & - & - & -  \\
MISE & - & - & - & - & -  \\ \hline
Type I error & - & - & - & - & -  \\ \hline
\end{tabular}
\caption{Mean-integrated squared error and type I error as a function of sampling rate for $\beta(s)$ given by (1) and (2) respectively.}
\label{tab:mise}
\end{table}

>>>>

\begin{table}[!th]
\begin{tabular}{c | c c c c c}
& \multicolumn{5}{c}{Sampling rate} \\ \cline{2-6}
 & 0.5 & 1 & 5 & 25 & 50 \\ \hline
Subsampling variance & (10,12) & - & - & - & - \\
Variance & (10,12) & - & - & - & - \\
Squared Bias & - & - & - & - & -  \\
MISE & - & - & - & - & -  \\ \hline
Type I error & - & - & - & - & -  \\ \hline
Avg runtime & - & - & - & - & - \\
\end{tabular}
\caption{Mean-integrated squared error and type I error as a function of sampling rate for $\beta(s)$ given by (1) and (2) respectively.}
\label{tab:mise}
\end{table}
